\documentclass[english]{article}
\usepackage{babel}
\usepackage[a4paper, total={6.5in, 9.5in}]{geometry}

\setlength{\parindent}{0em}
\setlength{\parskip}{1em}

\title{OpenSauce Project Plan}
\author{Jonni Koskela, Juuso Määttä, Juho Oja, Markus Suominen, Jussi Vaara}

\begin{document}
\maketitle

\subsection*{Project Goals}

Our final product will be a universally adaptable Android app that helps the
user evaluate their choices regarding personal transportation. It will
calculate scores for carbon, health, time cost and pleasure based on reliable
estimations and user input.

The primary objective is to get a general idea how to work as a team, and
practice using the tools required to build a legitimate, functioning
Android app. We hope that the end product will provide some degree of utility, but
also amusement, and hopefully makes people rethink how they move about in their
daily lives.

\subsection*{Core Tasks}

\begin{enumerate}
\item Create a business plan, perform project feasibility analysis
\item Define core functionality, come up with features and evaluate their
   usefulness vs. implementation cost
\item Create the basic data structures (classes) that are needed for the app to work
\item Design and implement a working user interface (emphasis on logic of use, not appearance)
\item Design a unified, tidy look for the app
\item Test the app in the wild with actual users
\item Write the documentation
\item Plan out and deliver the presentation
\end{enumerate}

\subsection*{Day-to-Day Activities and Tools}

Given the scheduling restraints, our team will have to work individually on
assigned tasks, which have been mutually agreed upon. Changes will submitted to
our GitHub and all work will be continually assessed by the whole team. Day-to-day
communication takes place through a dedicated WhatsApp group.

The primary tools will be a text editor of one's choosing and Android Studio.
Text file encoding should not matter too much, as only ASCII characters are
used. If the Euro symbol is needed for some reason, the files have to be
encoded as UTF-8 with UNIX newlines if possible (Android default).

\newpage
\subsection*{Division of Labor}
Members of the group have been assigned roles and titles, which are as follows:

\begin{tabular}{ p{18em} p{32em} }
Senior Developer & Markus Suominen\\
Usability Specialist & Juuso Määttä\\
Lead Artist & Jonni Koskela\\
Executive Producer & Jussi\\
Project Manager & Juho

\end{tabular}

Project Manager is responsible for all Moodle submissions.

\subsection*{Pitfalls and Exception Handling}
Project manager will be responsible for smooth project execution. If any
problems or roadblocks arise, he's the one to go to first. We do not expect
any significant challenges, but scheduling meetings with all 5 people present will
be practically impossible.

We are not particularly concerned about anyone dropping out of the group, as all
members possess the necessary skills to bring the project to a satisfactory state
of completion.

\end{document}
